Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-13 proposal/mprop.tex
Finish problem statement and almost complete research questions and contributions subsection

This research is trying to investigate the various components of a 
issue tracking system ticket and specific characteristics

@@

>>>>

This research is trying to investigate what makes for a high quality 
ticket. More specifically, we are looking into the various components 
of a ticket (e.g. summary, description, comments) and their characteristics
in order to infer what combination of such components or what specific
attributes help developers close the ticket quicker (i.e. time between
ticket creation and when it is marked as CLOSED or RESOLVED).

We believe that this study is valuable to the software engineering 
community because solving the issue/ticket quality problem will help
reduce both cost and effort in companies worldwide. 
Having a clear understanding of what attributes make for 
a high quality ticket will lead the project maintainers to write  
specific guidelines in the ticket creation form (maybe even create an 
automated system) that will help reporters include the most
important details and structure them accordingly (e.g. for a specific
type of project it might be essential to include stack traces so that
developers can locate the bugs quicker), thus reducing the developers
and triagers' effort as well as reducing costs for the companies.

Furthermore, our study might also increase the likelihood of people
reporting bugs or asking for features more often. Not having specific 
guidelines or an automated system when creating a ticket many 
non-technical users might be put off and give up creating the report. 
However, if the company would put up a form where all the information
needed can be very easily inserted, users might be more inclined 
to report bugs and create feature requests, thus increasing the 
software's overall quality on the long term.

@@

The main research question this study is trying to answer is 
what makes for a valuable, high quality?

However, as this is a broad research question, we have divided it into
two sub-research questions which, when combined, would yield the 
answer to our main research question:
  \begin{itemize}
    \item are there components which singularly affect the quality
      of a ticket (e.g. well written summary) or only combinations of them 
      (e.g. stack traces together with steps to reproduce)?
    \item how much do specific components or combinations of them 
      affect the quality of a ticket?
    \item can quality be inferred solely from the ticket or do we also
      need to consider the surrounding context (e.g. details related to
      the version control system)?
  \end{itemize}
